Distributed Nonlinear Feedback Design with Separable Control-Contraction Metrics

### 2017-05-31 R0V0.tex
Change notation of the plant graph by adding a subscript p

\mypara Let $N>0$ be an integer and consider the graph $\mathscr{G}$ defined by the set of vertices $\mathscr{V}=\mathbb{N}_{[1,N]}$ and a set of edges $\mathscr{E}\subset\mathbb{N}_{[1,N]}\times\mathbb{N}_{[1,N]}$. For each index $i\in\mathbb{N}_{[1,N]}$, system~\eqref{eq:general system} can be decomposed into smaller components as follows.
\begin{equation}\label{eq:subsystem}
	\dot{x}_i=f_i(x_i,\breve{x}_i)+b_i(x_i)u_i\;,
\end{equation}
where $\breve{x}_i\in\mathbb{R}^{\breve{n}_i}$ stands for the vector composed of states $x_j$ of systems that are adjacent to system~\eqref{eq:subsystem}. Given a graph $\mathscr{G}_c=(\mathbb{N}_{[1,N]},\mathscr{E}_c)$ that specifies a communication network. One of the objectives of this work is to design a feedback law $k_i^\ast=k_i(t,x_i,\vec{x}_i,X_i^\ast,\vec{X}_i^\ast,u_i^\ast)$ for \eqref{eq:subsystem} under the constraints defined by $\mathscr{G}_c$, where $\vec{x}_i\in\mathbb{R}^{\vec{n}_i}$ stands for the vector composed of states $x_j\in\mathbb{R}^{n_j}$, that are adjacent to system $i$, according to the set of edges $\mathscr{E}_c$.

@@

\mypara In the ``neighbor'' case, the communication network topology $\mathscr{G}_c$ has the same structure as the network system. Consequently, the set of edges $\mathscr{E}_c$ is defined as $\mathscr{E}_c=\mathscr{E}$.

@@

\mypara In the ``neighbor'' case, the topology of the controller is the same as of the network. More precisely, $\mathscr{G}_c=\mathscr{G}$. The solver took 57s to solve the set of matrix inequalities~\eqref{eq:main result}.

>>>>

\mypara Let $N>0$ be an integer and consider the graph $\mathscr{G}_p$ defined by the set of vertices $\mathscr{V}_p=\mathbb{N}_{[1,N]}$ and a set of edges $\mathscr{E}_p\subset\mathbb{N}_{[1,N]}\times\mathbb{N}_{[1,N]}$. For each index $i\in\mathbb{N}_{[1,N]}$, system~\eqref{eq:general system} can be decomposed into smaller components as follows.
\begin{equation}\label{eq:subsystem}
	\dot{x}_i=f_i(x_i,\breve{x}_i)+b_i(x_i)u_i\;,
\end{equation}
where $\breve{x}_i\in\mathbb{R}^{\breve{n}_i}$ stands for the vector composed of states $x_j$ of systems that are adjacent to system~\eqref{eq:subsystem}. Given a graph $\mathscr{G}_c=(\mathbb{N}_{[1,N]},\mathscr{E}_c)$ that specifies a communication network. One of the objectives of this work is to design a feedback law $k_i^\ast=k_i(t,x_i,\vec{x}_i,X_i^\ast,\vec{X}_i^\ast,u_i^\ast)$ for \eqref{eq:subsystem} under the constraints defined by $\mathscr{G}_c$, where $\vec{x}_i\in\mathbb{R}^{\vec{n}_i}$ stands for the vector composed of states $x_j\in\mathbb{R}^{n_j}$, that are adjacent to system $i$, according to the set of edges $\mathscr{E}_c$.

@@

\mypara In the ``neighbor'' case, the communication network topology $\mathscr{G}_c$ has the same structure as the network system. Consequently, the set of edges $\mathscr{E}_c$ is defined as $\mathscr{E}_c=\mathscr{E}_p$.

@@

\mypara In the ``neighbor'' case, the topology of the controller is the same as of the network. More precisely, $\mathscr{G}_c=\mathscr{G}_p$. The solver took 57s to solve the set of matrix inequalities~\eqref{eq:main result}.
